An elaborate data set on human gait and the effect of mechanical perturbations

### 2014-12-14 paper.tex
Fixed some units.

Early on, we discovered that the factory setup of the R-Link treadmill had a
vibration mode as low as 5 Hz that is detectable in the force measurements,
likely due to the flexible undercarriage and pitch motion mechanism. Trials 6-8
are affected by this vibration mode. During trials 9-15 the treadmill was
stabilized with wooden blocks. During, the remaining trials the treadmill was
stabilized with metal supports. See the Data Limitations Section for more
details.

@@

\section*{Data Limitations}
%
The data is provided in good faith with great attention to detail but as with
all data there are anomalies that may affect the use and interpretation of
results emanating from the data. The following list gives various notes and
warnings about the data that should be taken into account when making use of
it.
%
\begin{itemize}
  \item Be sure to read the notes in each meta data file for details about
    possible anomalies in that particular trial. Things such as marker dropout,
    ghost markers, and marker movement are the more prominent notes. Details
    about variations in the equipment on the day of the trial are also
    mentioned.
  \item The subject identification number 0 stands for "no subject" and was
    used whenever data was collected from the system with no subject on the
    treadmill, for example during the trials that were intended to be used for
    inertial compensation purposes. These trials play through the exact
    protocol as those with a human subject and the matching trials are
    indicated in the meta data. Matching unloaded trials were recorded on the
    same day as the loaded trials and is noted in the
    \verb|trial:files:compensation| section of the meta data file.
  \item Trials 1 and 2 were not recorded as part of this study. Those trial
    identification numbers were reserved for early data exploration from data
    collected in other studies.
  \item Trials 37, 38, and 39 do not exist. The numbers were accidentally
    skipped.
  \item Trials 9, 10, and 11 used a slightly different event definition where the
    calibration poses were not explicitly tagged by an event, yet the protocol
    was the identical to the following trials. The calibration pose will have
    to be determined manually.
  \item  Trials 6-15 have force measurements are affected by the treadmill
    vibration mode mentioned in the equipment section and the forces should be
    not be used. We include the trials because both the kinematic data is valid
    and trials 6-8 include lateral perturbations in addition to the
    longitudinal.
  \item During trials 9-15 we used wooden blocks to fix the treadmill to the
    concrete floor to eliminate the treadmill's low vibration mode
    (~5 hz). But these blocks seem to have corrupted the force plate
    measurements by imposing frictional stresses on the system. The force plate
    measurements should not be used from these trials, but the marker data is
    fine.
  \item Trials 6-8 use an early experimental protocol which divided the
    perturbation sections into three sections: longitudinal perturbations,
    lateral perturbations, and a combination of each. We then learned the
    treadmill had a low vibrational mode which significantly affects the force
    plate measurements, requiring us to eliminate the lateral perturbation
    motions. The force measurements during these trials are corrupted by this
    vibrational mode and should be used with caution or not at all.
  \item We did not record unloaded compensation trials for trials 9-15.
    Regardless, they would likely be useless due to the corruption from the
    wooden blocks.
  \item Trials 6-8 use a only the lower body marker set. The remaining trials
    are full body.
  \item The ankle joint torques computed from subject 9's data in trials 25-27
    are abnormal and should be used with caution or not at all. We were not
    able to locate the source of the error, but it is likely related to the
    force calibration.
\end{itemize}

>>>>

Early on, we discovered that the factory setup of the R-Link treadmill had a
vibration mode as low as 5\si{\hertz} that is detectable in the force measurements,
likely due to the flexible undercarriage and pitch motion mechanism. Trials 6-8
are affected by this vibration mode. During trials 9-15 the treadmill was
stabilized with wooden blocks. During, the remaining trials the treadmill was
stabilized with metal supports. See the Data Limitations Section for more
details.

@@

\section*{Data Limitations}
%
The data is provided in good faith with great attention to detail but as with
all data there are anomalies that may affect the use and interpretation of
results emanating from the data. The following list gives various notes and
warnings about the data that should be taken into account when making use of
it.
%
\begin{itemize}
  \item Be sure to read the notes in each meta data file for details about
    possible anomalies in that particular trial. Things such as marker dropout,
    ghost markers, and marker movement are the more prominent notes. Details
    about variations in the equipment on the day of the trial are also
    mentioned.
  \item The subject identification number 0 stands for "no subject" and was
    used whenever data was collected from the system with no subject on the
    treadmill, for example during the trials that were intended to be used for
    inertial compensation purposes. These trials play through the exact
    protocol as those with a human subject and the matching trials are
    indicated in the meta data. Matching unloaded trials were recorded on the
    same day as the loaded trials and is noted in the
    \verb|trial:files:compensation| section of the meta data file.
  \item Trials 1 and 2 were not recorded as part of this study. Those trial
    identification numbers were reserved for early data exploration from data
    collected in other studies.
  \item Trials 37, 38, and 39 do not exist. The numbers were accidentally
    skipped.
  \item Trials 9, 10, and 11 used a slightly different event definition where the
    calibration poses were not explicitly tagged by an event, yet the protocol
    was the identical to the following trials. The calibration pose will have
    to be determined manually.
  \item  Trials 6-15 have force measurements are affected by the treadmill
    vibration mode mentioned in the equipment section and the forces should be
    not be used. We include the trials because both the kinematic data is valid
    and trials 6-8 include lateral perturbations in addition to the
    longitudinal.
  \item During trials 9-15 we used wooden blocks to fix the treadmill to the
    concrete floor to eliminate the treadmill's low vibration mode
    (\~5\si{\hertz}). But these blocks seem to have corrupted the force plate
    measurements by imposing frictional stresses on the system. The force plate
    measurements should not be used from these trials, but the marker data is
    fine.
  \item Trials 6-8 use an early experimental protocol which divided the
    perturbation sections into three sections: longitudinal perturbations,
    lateral perturbations, and a combination of each. We then learned the
    treadmill had a low vibrational mode which significantly affects the force
    plate measurements, requiring us to eliminate the lateral perturbation
    motions. The force measurements during these trials are corrupted by this
    vibrational mode and should be used with caution or not at all.
  \item We did not record unloaded compensation trials for trials 9-15.
    Regardless, they would likely be useless due to the corruption from the
    wooden blocks.
  \item Trials 6-8 use a only the lower body marker set. The remaining trials
    are full body.
  \item The ankle joint torques computed from subject 9's data in trials 25-27
    are abnormal and should be used with caution or not at all. We were not
    able to locate the source of the error, but it is likely related to the
    force calibration.
\end{itemize}
